Title here

### 2020-07-21 analysis/paper/paper.tex
more results and agu

Figure \ref{fig:asymsam-timeseries} shows the resulting Asymmetric and
Symmetric time series corresponding to 700 and 30hPa. blablababla

@@

Figure \ref{fig:cross-correlation}a) show the cross-correlation across
levels for the Full SAM index. \ldots{}..

@@

\begin{sidewaysfigure}
\includegraphics{2d-regr-700-1} \caption[Seasonal regression patterns of geopotential height at 700 hPa with the Full, Asymmetric and Symmetric SAM]{Seasonal regression patterns of geopotential height at 700 hPa with the Full, Asymmetric and Symmetric SAM. The regression patterns for Asymmetric and Symmetric SAM are the result of one multiple regression using both indices, not of two simple regressions involving each index by itsef.}\label{fig:2d-regr-700}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\includegraphics{2d-regr-30-1} \caption[Seasonal regression patterns of geopotential height at 30 hPa with the Full, Asymmetric and Symmetric SAM]{Seasonal regression patterns of geopotential height at 30 hPa with the Full, Asymmetric and Symmetric SAM. The regression patterns for Asymmetric and Symmetric SAM are the result of one multiple regression using both indices, not of two simple regressions involving each index by itsef.}\label{fig:2d-regr-30}
\end{sidewaysfigure}

\subsubsection{Impacts}

\begin{sidewaysfigure}
\includegraphics{regr-air-season-1} \caption[Regression pattern of surface temperature with Asymmetric and Symmetric SAM]{Regression pattern of surface temperature with Asymmetric and Symmetric SAM. P-values smaller than 0.05 (controlling for Flase Detection Rate) as hatched areas.}\label{fig:regr-air-season}
\end{sidewaysfigure}

@@

\begin{figure}
\includegraphics{A4-1} \appendcaption{A4}{Trends for each index at each level. Shading indicates the 95\% confidence interval.}\label{fig:A4}
\end{figure}

>>>>

Figure \ref{fig:asymsam-timeseries} shows the resulting Asymmetric and
Symmetric time series corresponding to 700 and 30hPa. blablababla
\#FIXME

@@

Figure \ref{fig:cross-correlation}a) show the cross-correlation across
levels for the Full SAM index. \#FIXME

\begin{figure}
\includegraphics{trends-1} \caption[Trends for each index at each level]{Trends for each index at each level. Shading indicates the 95\% confidence interval.}\label{fig:trends}
\end{figure}

Figure \ref{fig:trends} shows normalised decadal trends for each index
for the whole period along with a 95\% interval in shading. There is a
statistically significant increase in positive SAM in the tropostphere
(panel a), which has been already documented in other studies (e.g.
\citet{fogt2020}). Panels b and c of Figure \ref{fig:trends} show that
this increase is evident only in the Symmetric component. This
distinction should prove useful when attributing trends in other
variables such as temperature and precipitation to trends in the SAM.

@@

\subsection{Impacts}

\subsubsection{Temperature}

\begin{sidewaysfigure}
\includegraphics{regr-air-season-1} \caption[Regression pattern of surface temperature with Asymmetric and Symmetric SAM]{Regression pattern of surface temperature with Asymmetric and Symmetric SAM. P-values smaller than 0.05 (controlling for Flase Detection Rate) as hatched areas. Gray areas have more than 15\% of missing data.}\label{fig:regr-air-season}
\end{sidewaysfigure}

Figure \ref{fig:regr-air-season} shows regression coefficients of each
index at 700 hPa with surface temperature for each trimester. It is
evident that the Asymmetric and Symmetric SAM indices are associated
with overall distinct temperature patterns which can be obscured when
using the Full SAM index. The Symmetric SAM signal is weaker than the
Asymmetric SAM, as evidenced by the relatively smaller and les
sstatistically significant regression coefficients in row 3 of Figure
\ref{fig:regr-air-season} compared with row 2.

In DJF (column a), the strong negative signal in the tropical Pacific in
panel a.1 is mostly associated with the Asymmetric component (panel
a.2), as is it largely absent in the Symmetric component (panel a.3).
Furthermore, the Asymmetric SAM is also asociated with low temperature
anomalies in the Indian ocean, but this signal is obscured by the
Symmetric variability and thus lost in the Full SAM. Over the
continents, the Asymmetric SAM is assoiated with negative temperature
anomalies which, again, mostly disappear in the Full SAM regression.

The patterns seen in MAM and JJA (columns b and c) are not robustly
significant in the sense that there are no areas with p-values below
0.05 when controlling for FDR following \citet{wilks2016}. Nevertheless,
it is interesting to note that in both trimesters, the sign of the
regression is consistently flipped between the Asymmetric and Symmetric
regressions. In South America, for example, the Asymmetric SAM is
associated with positive temperature anomalies in MAM and negative
temperature anomales in JJA, while the oposite is the case for the
Symemtric SAM.

Finally, in SON (column d), there is no significant temperature signal
associated with the Symmetric SAM (panel d.3), while the Asymmetric SAM
shows a relatively robust signal in the equatorial Pacitic, Australia,
and even Southeast South America. This strong signals are reduced in
intensity in panel a.3.

\subsubsection{Precipitation}

@@
